% Introduction file, to be included in rasd.tex

\section{Introduction}
\label{sect:introduction}
\subsection{Purpose}
This document represents the RASD (Requirement Analysis and Specification Document).

The aim of this document is to completely describe the system in terms of functional and non-functional requirements, analyse the many different ways that the users may behave in order to model the system, show the constraints and the limit of the software and indicate the typical use cases that will
occur after the release.
 
This document is the baseline for project planning and estimation of size, cost, schedule. It can be also an useful starting point for the legal binding contract.

\subsection{Scope}
\subsubsection{Problem description}
CLup is a software-to-be that will help stores and customers preventing dangerous crowds during shopping due to the current Covid-19 Pandemic. This system should offer the possibility to line up from home for stores while still allowing to physically line up for stores. Moreover, it should offer the possibility to book a visit for a chosen store and get notifications about stores occupancy during the week.
The system should also allow store managers to add their stores to the system and monitor entrances.

The application has to be easy-to-use, scalable and reliable.
\input{introduction/goals}
\input{introduction/phenomena}
\input{introduction/Def}

\subsection{Revision history}
\begin{center}
	\begin{tabular}{c | c | c}	
		Version & Date & Comment \\ \hline
		1.0 & 2020-12-22 & First release
	\end{tabular}
\end{center}


\subsection{Reference documents}
R\&DD Assignment AY 2020-2021, \textit{Software Engineering 2's BeeP page}

\subsection{Document Structure}
This document is composed of the following parts:
\begin{itemize}[itemsep=-1mm, topsep=-1mm]
	\item \textbf{Section \ref{sect:introduction}} is an introduction to the document and offers an overview of the project, describing what its goals are and giving pointers to the following sections
	\item \textbf{Section \ref{sect:overview}} gives an overview of the project, showing its usages and its domain. Actors are also stated in this section, alongside state and class diagrams
	\item \textbf{Section \ref{sect:requirements}} identifies the system's requirements, both functional and non-functional, then presents the application's use cases and its sequence diagrams
	\item \textbf{Section \ref{sect:alloy}} contains an Alloy model of the system with proofs of consistency
	\item \textbf{Section \ref{sect:effort}} reports the hours spent by this group's components and the tool used during the development of this document 
\end{itemize}